The Analysis of Pluralistic Ignorance of Married Men in Saudi Arabia on Women Working Outside of Home (WWOH) ^[Code and data are available at: https://github.com/YcartXin/Analysis-of-Men-in-Saudi-Arabia-on-WWOH]

### 2024-02-13 paper/paper.qmd
updated scripts and references

## Data source and collection
The data used in this analysis - Main Experiment of Saudi Arabia men on WWOH and their beliefs of others’ opinions  - is sourced from the replication package provided by Bursztyn et.al (year). The data was collected by the researchers in the original paper through an experiment and repeated surveys with a treatment group and a control group. This analysis will be carried out in R [6] using packages tidyverse [7], knitr [8], dplyr [9], ggplot2 [10], knitr [8], and here [11]. Although the experiment claims to have only recruited men who are married, the data shows otherwise and thus some data points will be further removed from the analysis. The paper was published in the American Economic Review 2020, 110(10) issue between pages 2997-3029 (). The data was similarly uploaded at the same time and has not been updated since.

@@

```{r}
#| echo: false
#| label: tbl-sum
#| fig-cap: Summary Statistics on Saudi Arabian Men Participated in Survey on WWOH

summary_stats <- wwoh_data |>
  group_by(condition2) |>
  summarize(
    Observations = n(),
    Mean_age = mean(age, na.rm =TRUE),
    Mean_children = mean(children, na.rm = TRUE),
    Percent_college = sum(college_deg, na.rm = TRUE)/n()*100,
    Percent_employed = sum(employed_now, na.rm = TRUE)/n()*100,
  ) |>
  bind_rows()|>
  mutate(group = c("Control", "Treatment")) |>
  select(condition2, everything())

@@

# References

>>>>

## Data source and collection
The data used in this analysis - Main Experiment of Saudi Arabia men on WWOH and their beliefs of others’ opinions  - is sourced from the replication package provided by Bursztyn et.al (year). The data was collected by the researchers in the original paper through an experiment and repeated surveys with a treatment group and a control group. This analysis will be carried out in **R** @citeR using packages **tidyverse** @tidyverse, **knitr** @knitr, **dplyr** @dplyr, **ggplot2** @ggplot2, **knitr** @knitr, **here ** @here. Although the experiment claims to have only recruited men who are married, the data shows otherwise and thus some data points will be further removed from the analysis. The paper was published in the American Economic Review 2020, 110(10) issue between pages 2997-3029 (). The data was similarly uploaded at the same time and has not been updated since.

@@

```{r}
#| echo: false
#| label: tbl-sum
#| fig-cap: Summary Statistics on Men Who Participated in the Main Experiment

summary_stats <- wwoh_data |>
  group_by(condition2) |>
  summarize(
    Observations = n(),
    Age = mean(age, na.rm =TRUE),
    Children = mean(children, na.rm = TRUE),
    "College(%" = sum(college_deg, na.rm = TRUE)/n()*100,
    "Employed(%)" = sum(employed_now, na.rm = TRUE)/n()*100,
  ) |>
  bind_rows()|>
  mutate(group = c("Control", "Treatment")) |>
  select(condition2, everything())

@@
